%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	11pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font
\usepackage{hyperref}

\name{Tagir Safin}

\address{Belgrade, Serbia}
\address{safintagirn@gmail.com}
\address{\url{https://github.com/zilzilok}}


\begin{document}
	
\begin{rSection}{Summary}
	
Software Engineer with 4 years of experience, specializing in Java and Kotlin. As a member of the B2B team in Marketplace dedicated to enhancing services for both customers and sellers, I developed software solutions to improve platform interactions, streamline processes, and elevate overall user satisfaction.

I like drinking tea, playing the drums, and both watching and playing basketball.
\end{rSection}

\begin{rSection}{Experience}

\begin{rSubsection}{Yandex}{April 2021 - Present}{Software Engineer}{Moscow, Belgrade}
	\item Worked in Yandex Market (Marketplace) B2B team. Developed and implemented features to improve service quality for sellers and customers of the marketplace. Took major roles in multiple projects.
	\item Implemented compliance and quality controls in customer–seller communication channels. As a result, identified many partners with issues (250 in a short period).
	\item Increased seller onboarding and boosted the success rate from 65\% to 85–90\%, adding 500 partners weekly without compromising order quality.
	\item Reduced the outflow of sellers, contributing an additional 0.5\% to GMV (Gross Merchandise Value) growth.
	\item Led to more reliable, high-performing microservices. For example, found and fixed a problem in a service that helped reduce database load (CPU) and cut service response time by half.
\end{rSubsection}
\end{rSection}

\begin{rSection}{Education}
	\textbf{Higher School of Economics, Faculty of Computer Science} \hfill {September 2018 - July 2022} \\
	\textit{Bachelor of Science in Software Engineering} \hfill \textit{Moscow, Russia}
	
	\textbf{Graduate Projects:} Business Processes Automation App Using BPM Technologies
	
	\textbf{GPA:} 7.57/10
\end{rSection}


\begin{rSection}{Technical Strengths}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Computer Languages & Java, Kotlin (Spring Framework, Gradle, JUnit, Mockito, AssertJ) \\
		Databases & PostgreSQL, Clickhouse \\
		Other Tools & AWS, Apache Kafka, Docker, Unix, Git
	\end{tabular}

\end{rSection}


\begin{rSection}{Languages}
	
	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Russian & Native \\
		English & Upper intermediate
	\end{tabular}
	
\end{rSection}

\end{document}
